---
title: "Statistique sur les donnée"
execute:
  echo: true    # Garde ton code visible (si tu le souhaites)
  warning: false # Cache les messages orange (conflits)
  message: false # Cache les messages de chargement (tidyverse)
---

About this site

```{r}
library(tidyverse) ; # loads core libraries for data manipulation
catastrophes <- read_csv("donnee et data frame final/catastrophes.csv") ; # imports catastrophes data
synop_csv <- read_csv("donnee et data frame final/synop.csv.gz") ; # imports synop data
```

You need to end up with a data set containing monthly data for the following variables: • year • month • average temperature of the month in Celsius degrees • gap between the month’s temperature (variable above) and the overall average temperatures for this month (across all years) • total number of natural disasters in France for this month • total number of damages, in dollars, in France for this month • total number of deaths in France for this month

```{r}
library(data.table) ; # loads package for fast data reading
library(R.utils) ; # activates support for gz compressed files
data <- fread("donnee et data frame final/synop.csv.gz") ; # reads synop file from data folder
```
